\documentclass[12pt, titlepage]{article}

\usepackage{amsmath, mathtools}

\usepackage[round]{natbib}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[section]{placeins}
\usepackage{caption}
\usepackage{fullpage}

\hypersetup{
bookmarks=true,     % show bookmarks bar?
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with linkbordercolor)
citecolor=blue,      % color of links to bibliography
filecolor=magenta,  % color of file links
urlcolor=cyan          % color of external links
}

\usepackage{array}

%\input{../../Comments}

\newcommand{\progname}{Program Name}

\begin{document}

\title{Module Interface Specification for Library of Linear Algebraic Equation Solver}

\author{Devi Prasad Reddy Guttapati}

\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

See SRS Documentation at:  \url{https://github.com/deviprasad135/CAS741/blob/master/Doc/SRS/CA.pdf}


\newpage

\tableofcontents

\newpage

\pagenumbering{arabic}

\section{Introduction}

The following document details the Module Interface Specifications for
%\wss{Fill in your project name and description}

Complementary documents include the System Requirement Specifications
and Module Guide.  The full documentation and implementation can be
found at \url{https://github.com/deviprasad135/CAS741}.  %\wss{provide the url for your repo}

\section{Notation}

%\wss{You should describe your notation.  You can use what is below as
  %a starting point.}

The structure of the MIS for modules comes from \citet{HoffmanAndStrooper1995},
with the addition that template modules have been adapted from
\cite{GhezziEtAl2003}.  The mathematical notation comes from Chapter 3 of
\citet{HoffmanAndStrooper1995}.  For instance, the symbol := is used for a
multiple assignment statement and conditional rules follow the form $(c_1
\Rightarrow r_1 | c_2 \Rightarrow r_2 | ... | c_n \Rightarrow r_n )$.

The following table summarizes the primitive data types used by \progname. 

\begin{center}
\renewcommand{\arraystretch}{1.2}
\noindent 
\begin{tabular}{l l p{7.5cm}} 
\toprule 
\textbf{Data Type} & \textbf{Notation} & \textbf{Description}\\ 
\midrule
character & char & a single symbol or digit\\
integer & $\mathbb{Z}$ & a number without a fractional component in (-$\infty$, $\infty$) \\
natural number & $\mathbb{N}$ & a number without a fractional component in [1, $\infty$) \\
real & $\mathbb{R}$ & any number in (-$\infty$, $\infty$)\\
\bottomrule
\end{tabular} 
\end{center}

\noindent
The specification of \progname \ uses some derived data types: sequences, strings, and
tuples. Sequences are lists filled with elements of the same data type. Strings
are sequences of characters. Tuples contain a list of values, potentially of
different types. In addition, \progname \ uses functions, which
are defined by the data types of their inputs and outputs. Local functions are
described by giving their type signature followed by their specification.

\section{Module Decomposition}

The following table is taken directly from the Module Guide document for this project.

\begin{table}[h!]
\centering
\begin{tabular}{p{0.3\textwidth} p{0.6\textwidth}}
\toprule
\textbf{Level 1} & \textbf{Level 2}\\
\midrule

{Hardware-Hiding} & ~ \\
\midrule

\multirow{3}{0.3\textwidth}{Behaviour-Hiding} 
& Input Computing Module\\
& Output computing Module\\
& Library of Linear Algebraic Equation Solver Module\\


\midrule

\multirow{2}{0.3\textwidth}{Software Decision}  & Gaussian Elimination Module\\

& Gauss-Jordan Elimination Module\\


\bottomrule

\end{tabular}
\caption{Module Hierarchy}
\label{TblMH}
\end{table}

\newpage
~\newpage

\section{MIS of {Library of Linear Algebraic Equation Solver Module}} \label{llaem} %\wss{Use labels for cross-referencing}

\subsection{Module}

LLAES

%\wss{Short name for the module}

\subsection{Uses}
This is the top level module which interacts with the external program. This module uses all other modules in the library. 


\subsection{Syntax}

\subsubsection{Exported Access Programs}

\begin{center}
\begin{tabular}{p{2cm} p{4cm} p{4cm} p{2cm}}
\hline
\textbf{Name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions} \\
\hline
Linear Algebraic Equation Methods & Linear Algebraic Equation Method & - & - \\
A & $n \times n$ matrix $\in$ $\mathbb{R}$ and n $> 0$ & - & - \\
b & $1 \times n$ matrix $\in$ $\mathbb{R}$ and n $> 0$ & - & - \\
\hline
\end{tabular}
\end{center}

\subsection{Semantics}

\subsubsection{State Variables}


\subsubsection{Access Routine Semantics}

\noindent %\wss{accessProg}():
\begin{itemize}
\item transition: %\wss{if appropriate} 
\item output: %\wss{if appropriate} 
\item exception: %\wss{if appropriate} 
\end{itemize}

\section{MIS of {Gaussian Elimination  Module}} \label{gem}

\subsection{Module}

GEM

%\wss{Short name for the module}

\subsection{Uses}
This module is used to solve the system of Linear Algebraic Equations.


\subsection{Syntax}

\subsubsection{Exported Access Programs}

\begin{center}
\begin{tabular}{p{2cm} p{4cm} p{4cm} p{2cm}}
\hline
\textbf{Name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions} \\
\hline

A & $n \times n$ matrix $\in$ $\mathbb{R}$ and n $> 0$ & - & - \\
b & $1 \times n$ matrix $\in$ $\mathbb{R}$ and n $> 0$ & - & - \\
\hline
\end{tabular}
\end{center}

\subsection{Semantics}
Pseudo Code

for $k = 1$ to $n-1$

find a pivot p such that

$|a_{pk}| \geq |a_{ik}|$ for $K \leq i \leq n$

if $|a_{pk}| = 0$ do

return "Singular Matrix"

end the entire loop

else interchange row p and k

for $i = k+1$ to $n$

$factor_{ik} = \dfrac{a_{ik}}{a_{kk}}$

for $j = k+1$ to $n$

$a_{ij} = a_{ij} - factor_{ik} * a_{kj}$

end for

end for

end for

$x_n = \dfrac{b_n^{'}}{a_{nn}} $

for i in n-1 to 1

for j in i+1 to n

$sum = a_{ij}x_j$

end for

$x_i = \dfrac{b_n^{'} - sum} {a_{ii}}$

end for

\subsubsection{State Variables}


\subsubsection{Access Routine Semantics}

\noindent %\wss{accessProg}():
\begin{itemize}
\item transition: %\wss{if appropriate} 
\item output: %\wss{if appropriate} 
\item exception: %\wss{if appropriate} 
\end{itemize}

\section{MIS of {Gauss-Jordan Elimination  Module}} \label{gjm}

\subsection{Module}

GJEM

%\wss{Short name for the module}

\subsection{Uses}
This module is used to solve the system of Linear Algebraic Equations.


\subsection{Syntax}

\subsubsection{Exported Access Programs}

\begin{center}
\begin{tabular}{p{2cm} p{4cm} p{4cm} p{2cm}}
\hline
\textbf{Name} & \textbf{In} & \textbf{Out} & \textbf{Exceptions} \\
\hline

A & $n \times n$ matrix $\in$ $\mathbb{R}$ and n $> 0$ & - & - \\
b & $1 \times n$ matrix $\in$ $\mathbb{R}$ and n $> 0$ & - & - \\
\hline
\end{tabular}
\end{center}

\subsection{Semantics}

Pseudo Code

for $k = 1$ to $n-1$

find a pivot p such that

$|a_{pk}| \geq |a_{ik}|$ for $K \leq i \leq n$

if $|a_{pk}| = 0$ do

return "Singular Matrix"

end the entire loop

else interchange row p and k

for $i = k+1$ to $n$

$factor_{ik} = \dfrac{a_{ik}}{a_{kk}}$

for $j = k+1$ to $n$

$a_{ij} = a_{ij} - factor_{ik} * a_{kj}$

end for

end for

end for

Assuming that the matrix is not singular

for k = n to 2

for i = k+1 to 1

$factor_{ik} = \dfrac{a_{ik}}{a_{kk}}$

for j = k-1 to 1

$a_{ij} = a_{ij} - factor_{ik} * a_{kj}$

end for

end for

end for

for i in 1 to n

$x_i = \dfrac{b_n^{'}} {a_{ii}}$

end for



\subsubsection{State Variables}


\subsubsection{Access Routine Semantics}

\noindent %\wss{accessProg}():
\begin{itemize}
\item transition: %\wss{if appropriate} 
\item output: %\wss{if appropriate} 
\item exception: %\wss{if appropriate} 
\end{itemize}


\newpage

\bibliographystyle {plainnat}
\bibliography {../../../ReferenceMaterial/References}

\newpage

\section{Appendix} \label{Appendix}

%\wss{Extra information if required}

\end{document}
